It's Never Too Late To Learn\\ \emph{Using Online Machine Learning in Distributed Systems}

### 2016-01-22 writeups/msr_workshop/paper.tex
Section 2 mods

Decisions made by an ML agent in distributed system are likely to rely on input
data collected from diverse and physically distributed components. As a result,
the input to the learning loop might be stale or inconsistent. What could be
done to mitigate those issues while making reasonable real-time decisions?
Additionally, the decisions outputted by the learning agent need to be executed
by diverse and distributed components. How could routine distributed systems
issues such failures and delays in an asynchronous setting affect the learning
system?

@@

- In general should be composable if at each level can define decision and reward,
and exploration randomization is different at each level

@@

What features of the run-time system are important to the ML agent? How can they
be captured effectively? Can the ML agent learn from incomplete data? For
example, if an ML agent needs to make decisions regarding performance
optimization, would ignoring garbage collection activities or the VMM result in
corrupting the learned model? How sensitive should the learner be?

- quesiton of what features to include is there, but being conservative usually the right
way to go
- bigger quesiton is how ml component deals with omissions and other problems. Separate
into failure sections? Yeah, replace this with ``failures'' and move feature selection stuff
down to last section

\subsection*{Randomization}

An ML agent can be trained offline with pre-labeled data. However, is this
possible in the context of distributed systems? An online learning systems is
more logical in this context, however, how do we quantify the costs of
exploration vs exploitation of learned strategies?

- Probably omit this, or replace with ``Randomization''. Basically, we already know
that exploratoin-exploitation is the right approach, and that will be encapsulated
by the ML component (its decisions will reflect this, and it will take care of
computing probabilities etc.). But there's an interesting point about inherent randomization
in systems

>>>>

Decisions made by an ML agent in distributed system are likely to rely on input
data collected from diverse and physically distributed components. As a result,
the input to the learning loop might be stale or inconsistent. What could be
done to mitigate those issues while making reasonable real-time decisions?
Additionally, the decisions outputted by the learning agent need to be executed
by diverse and distributed components. How could routine distributed systems
issues such as message delays in an asynchronous setting affect the learning
system?

@@

%% Sid:
%% In general should be composable if at each level can define decision and reward,
%% and exploration randomization is different at each level

@@

Failures are an expected occurrence in every distributed system. How do learning
systems cope with data omission or inability to execute decisions due to
failures? Can the ML agent learn from incomplete or potentially corrupt data?
How sensitive should the learner be to transient conditions in the system?

%% What features of the run-time system are important to the ML agent? How can they
%% be captured effectively? Can the ML agent learn from incomplete data? For
%% example, if an ML agent needs to make decisions regarding performance
%% optimization, would ignoring garbage collection activities or the VMM result in
%% corrupting the learned model? How sensitive should the learner be?
%% 
%% - quesiton of what features to include is there, but being conservative usually the right
%% way to go
%% - bigger quesiton is how ml component deals with omissions and other problems. Separate
%% into failure sections? Yeah, replace this with ``failures'' and move feature selection stuff
%% down to last section

%% Hussam: Sid, I don't understand what you mean by randomization in this context
%% So I am taking this subsection out.
%% \subsection*{Randomization}
%% 
%% An ML agent can be trained offline with pre-labeled data. However, is this
%% possible in the context of distributed systems? An online learning systems is
%% more logical in this context, however, how do we quantify the costs of
%% exploration vs exploitation of learned strategies?
%% 
%% - Probably omit this, or replace with ``Randomization''. Basically, we already know
%% that exploratoin-exploitation is the right approach, and that will be encapsulated
%% by the ML component (its decisions will reflect this, and it will take care of
%% computing probabilities etc.). But there's an interesting point about inherent randomization
%% in systems
%%
